Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-16 analysis/paper/paper.Rmd
more notes and thoughts from Anna...

Table 2. Monitoring scenarios adapted from [@rettie_summary_2017].
```{r}
tbl <- "Years|Initial collars|Min collars|cow multiplier|collaring month|collar duration
3|25|25|3|1|3
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```
TO DO: fill in set of monitoring scenarios when we have decided what they are.
*Anna thinking about this...

>>>>

Table 2. Monitoring scenarios adapted from [@rettie_summary_2017]. *maybe we could remove the last couple columns if they're not things we're going to be varying...? (same for min collars if the same as init?)
```{r}
tbl <- "Years|Initial collars|Min collars|cow multiplier|collaring month|collar duration
3|25|25|3|1|3
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```
TO DO: fill in set of monitoring scenarios when we have decided what they are.
*Anna thinking about this...
